---
title: "Advanced Usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Advanced Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Grid search with `run_power_grid()`

When exploring power across multiple effect sizes, estimators, or outcomes,
use `run_power_grid()`:

```{r grid, eval=FALSE}
library(staggeredpower)
data(nfs_panel)

results <- run_power_grid(
  data_clean = nfs_panel,
  outcome = c("clearance_rate", "assault_rate"),
  unit_var = "state",
  time_var = "year",
  group_var = "treatment_year",
  treat_ind_var = "treated",
  pta_type = "imputation",
  percent_effect = seq(1.05, 1.20, 0.05),
  models_to_run = c("imputation"),
  n_sims = 50
)
```

## YAML configuration

For complex grid specifications, define parameters in a YAML file:

```{r yaml, eval=FALSE}
# config.yaml example:
# outcome:
#   - clearance_rate
#   - assault_rate
# percent_effect:
#   min: 1.05
#   max: 1.20
#   step: 0.05

config <- load_config("config.yaml")
```

## Noise engines

staggeredpower provides configurable noise for counterfactual generation:

| Engine | Description | Use when |
|--------|-------------|----------|
| `"none"` | Deterministic (no noise) | Quick benchmarks, debugging |
| `"iid"` | IID Normal shocks | Standard power analysis |
| `"ar1"` | AR(1) per unit | Persistent unit-level shocks |
| `"ar1_common"` | AR(1) + common shocks | Calendar-year correlation |
| `"ar1_anchored"` | AR(1) + ATT-anchored | Realistic correlation structure |

```{r noise, eval=FALSE}
# Compare deterministic vs stochastic
result_det <- run_power_analysis(
  data_clean = nfs_panel, outcome = "clearance_rate",
  unit_var = "state", time_var = "year",
  group_var = "treatment_year", treat_ind_var = "treated",
  percent_effect = 1.10, pta_type = "imputation",
  models_to_run = "imputation", n_sims = 1,
  noise_spec = list(engine = "none")
)

result_ar1 <- run_power_analysis(
  data_clean = nfs_panel, outcome = "clearance_rate",
  unit_var = "state", time_var = "year",
  group_var = "treatment_year", treat_ind_var = "treated",
  percent_effect = 1.10, pta_type = "imputation",
  models_to_run = "imputation", n_sims = 50,
  noise_spec = list(engine = "ar1")
)
```

## Pre-trend testing

Assess whether pre-treatment trends are parallel:

```{r pretrend, eval=FALSE}
pretrend <- compute_pretrend_wald_test(
  data = nfs_panel,
  outcome_var = "clearance_rate",
  time_var = "year",
  id_var = "state",
  group_var = "treatment_year",
  cluster_var = "state"
)
pretrend
```

## Custom adapters

Register your own estimator:

```{r custom-adapter, eval=FALSE}
my_adapter <- estimator_adapter(
  name = "my_estimator",
  fit_fn = function(data, outcome_var, time_var, id_var, group_var, ...) {
    # Your estimation code here
  },
  extract_fn = function(result, ...) {
    standard_estimate(att = result$coef, se = result$se)
  }
)
register_adapter(my_adapter)
```

## Parallel processing

For large simulations, register a parallel backend:

```{r parallel, eval=FALSE}
library(doParallel)
cl <- makeCluster(detectCores() - 1)
registerDoParallel(cl)

# Now run_power_analysis() and run_power_grid() use all cores
result <- run_power_analysis(...)

stopCluster(cl)
```

Without `foreach`/`doParallel` installed, the package automatically falls back
to sequential `lapply` execution.
