---
title: "Getting Started with staggeredpower"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with staggeredpower}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Why power analysis for staggered DiD?

Staggered difference-in-differences (DiD) designs are common in policy evaluation,
where different units adopt a treatment at different times. Modern heterogeneity-robust
estimators (Callaway & Sant'Anna 2021, Borusyak et al. 2024, Gardner 2022) address
bias from treatment effect heterogeneity, but their statistical power properties
are less well understood.

`staggeredpower` fills this gap by simulating the data-generating process under
controlled conditions: it enforces parallel trends on your actual data, injects
treatment effects of a specified size, and estimates DiD models to compute
rejection rates. This lets you answer: "Given my panel structure, how large
must the effect be for my estimator to detect it?"

## Quick example

```{r load}
library(staggeredpower)
data(nfs_panel)
str(nfs_panel)
```

The `nfs_panel` dataset contains state-level panel data with staggered adoption
of non-fatal strangulation laws.

### Running a basic power analysis

```{r basic-power, eval=FALSE}
# Register parallel backend for speed (optional)
# library(doParallel)
# cl <- makeCluster(detectCores() - 1)
# registerDoParallel(cl)

result <- run_power_analysis(
  data_clean = nfs_panel,
  outcome = "clearance_rate",
  unit_var = "state",
  time_var = "year",
  group_var = "treatment_year",
  treat_ind_var = "treated",
  percent_effect = 1.10,
  pta_type = "imputation",
  models_to_run = c("imputation"),
  n_sims = 50,
  noise_spec = list(engine = "iid")
)

# View power results
result$final_power
```

### Interpreting results

The output includes:
- `power`: Share of simulations where the effect is statistically significant (|t| > 1.96)
- `mean_att`: Average estimated treatment effect across simulations
- `mean_se`: Average standard error
- `percent_effect`: The multiplicative effect size used (1.10 = 10% increase)

## Choosing an estimator

staggeredpower supports multiple heterogeneity-robust estimators via adapters:

| Adapter | Estimator | Required Package |
|---------|-----------|-----------------|
| `adapter_imputation()` | Borusyak et al. (2024) | `didimputation` |
| `adapter_cs()` | Callaway & Sant'Anna (2021) | `did` |
| `adapter_did2s()` | Gardner (2022) | `did2s` |
| `adapter_etwfe_poisson_glm()` | Wooldridge (2023) ETWFE | (built-in via `fixest`) |

Install only the packages you need:
```{r install-adapters, eval=FALSE}
install.packages("didimputation")  # for adapter_imputation
install.packages("did")            # for adapter_cs
```

## Next steps

See `vignette("advanced-usage")` for grid search, noise engines, and custom adapters.
